---
title: "Papayar"
author: "John Muschelli"
date: "July 15, 2016"
bibliography: JSM_2016.bib
output:
  ioslides_presentation:
    self_contained: false
    includes:
      in_header: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
```

## Problem: Images are 3D: Brain

```{r plot}
library(fslr)
img = mni_img(brain = TRUE)
img = dropEmptyImageDimensions(img)
writenii(img, "reduced_mni.nii.gz")
ortho2(img)
```

## Solution: What we want

```{r div, results='asis'}
library(papayar)
x = papaya_div()
cat(x)
```

## Let's make it interactive!

1. What is the value added?
2. Is it necessary? 
3. How could I first incorporate it in a static way (e.g. journals)
    - When that fails go interactive
    
Many times it's to display results.


## First Attempt: Use manipulate

The `manipulate` package [@manipulate] from RStudio can add 

- Images Rendering is slow
- Manipulate package!
- Problem is Image
- too much backend
- Use JS that already exists
 

## What is an image

- 3-dimensional array

## Lessons Learned

- Use other people's stuff
- Porting to R can help a communithy
    - not always so straightforward
    - Functionality at the whim of the maintainer
    - not std R
- htmlwidgets is great
    - not always super easy for a user to cram into
    


## Bibliography
